A Fast Unified Model for Parsing and Sentence Understanding

### 2016-06-07 writing/hard_stack_paper/paper.tex
Tidying.
Figure placement tweak.
Footnote format fix

\usepackage[leqno, fleqn]{amsmath}
\usepackage[breaklinks, colorlinks, linkcolor=black, urlcolor=black, citecolor=black, draft]{hyperref}
\usepackage{natbib}
% \usepackage{times}
\usepackage{newtxtext,newtxmath}
\usepackage{latexsym}
% \setlength\titlebox{7.5cm}    % Expanding the titlebox

@@

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lrrrr}
    \toprule
Model                   & Params.    & Trans. acc. (\%)  &   Train acc. (\%)  &   Test acc. (\%) \\
\midrule
\multicolumn{5}{c}{\textbf{Previous non-NN results}}\\
Lexicalized classifier \citep{snli:emnlp2015}
                        & ---                & ---                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{\textbf{Previous sentence encoder-based NN results}}\\
100D LSTM encoders \citep{snli:emnlp2015}
                        & 221k               & ---               &   84.8   &   77.6      \\
1024D pretrained GRU encoders \citep{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & ---              &   98.8   &   81.4       \\
300D Tree-based CNN encoders \citep{mou2015recognizing}
                        & 3.5m                & ---             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{\textbf{Our results}}\\
300D LSTM RNN encoders         & 3.0m                  & ---                &   83.9      &   80.6       \\
300D SPINN-PI-NT (\ii{parsed input, no tracking}) encoders
                        & 3.4m                  & ---                &   84.4      &   80.9       \\
300D SPINN-PI (\ii{parsed input}) encoders
                        & 3.7m                  & ---                &   89.2      &   \textbf{83.2}       \\
300D SPINN (unparsed input) encoders
                        & 2.7m                  & 92.4           &   87.2    &   82.6      \\
% \result{300D SPINN-PI, sequence-based attn.   }
%                         & ?                  & --                &   ?      &   86.3dv         \\
% \result{300D SPINN-PI, tree-based attn. }
%                         & ?                  & --                &   ?      &   \textbf{?}\\
% \midrule
% \multicolumn{5}{c}{Other previous NN results}\\
% \midrule
% 100D LSTM w/ word-by-word attention \citep{rocktaschel2015reasoning}
%                         & 252k               & --              &   85.3   &   83.5       \\
% 300D mLSTM word-by-word attention model \citep{DBLP:journals/corr/WangJ15b}
%                         & 1.9m               & --             &   92.0   &   86.1      \\
% 300D LSTMN with deep attention fusion \citep{cheng2016long}
%                         & 1.4m               & --                &   92.3   &   \textbf{89.1}      \\
    \bottomrule
  \end{tabular}
\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params.\ is the approximate number of trained parameters (excluding word embeddings for all models). Trans.\ acc.\ is the model's accuracy in predicting parsing transitions at test time. Train and test are SNLI classification accuracy.}
\end{table*}

@@

Because this paper aims to introduce a general purpose model for sentence encoding, we do not pursue the use of soft attention \citep{bahdanau2014neural,rocktaschel2015reasoning}, despite its demonstrated effectiveness on the SNLI task.\footnote{Attention-based models like \citet{rocktaschel2015reasoning,wang2015learning} and the unpublished \citet{cheng2016long} have shown accuracies as high as 86.3\% on SNLI, but are more narrowly engineered to suit the task, and do not yield sentence encodings.} However, we expect that it should be possible to productively combine our model with soft attention to reach state-of-the-art performance.

>>>>

\usepackage[leqno, fleqn]{amsmath}
\usepackage[breaklinks, colorlinks, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}
\usepackage{natbib}
% \usepackage{times}
\usepackage{newtxtext,newtxmath}
\usepackage{latexsym}
% \setlength\titlebox{7.5cm}    % Expanding the titlebox

@@

\begin{table*}[t]
  \centering\small
  \begin{tabular}{lrrrr}
    \toprule
Model                   & Params.    & Trans. acc. (\%)  &   Train acc. (\%)  &   Test acc. (\%) \\
\midrule
\multicolumn{5}{c}{\textbf{Previous non-NN results}}\\
Lexicalized classifier \citep{snli:emnlp2015}
                        & ---                & ---                    &   99.7   &   78.2      \\
\midrule
\multicolumn{5}{c}{\textbf{Previous sentence encoder-based NN results}}\\
100D LSTM encoders \citep{snli:emnlp2015}
                        & 221k               & ---               &   84.8   &   77.6      \\
1024D pretrained GRU encoders \citep{DBLP:journals/corr/VendrovKFU15}
                        & 15m                & ---              &   98.8   &   81.4       \\
300D Tree-based CNN encoders \citep{mou2015recognizing}
                        & 3.5m                & ---             &   83.4   &   82.1       \\
\midrule
\multicolumn{5}{c}{\textbf{Our results}}\\
300D LSTM RNN encoders         & 3.0m                  & ---                &   83.9      &   80.6       \\
300D SPINN-PI-NT (\ii{parsed input, no tracking}) encoders
                        & 3.4m                  & ---                &   84.4      &   80.9       \\
300D SPINN-PI (\ii{parsed input}) encoders
                        & 3.7m                  & ---                &   89.2      &   \textbf{83.2}       \\
300D SPINN (unparsed input) encoders
                        & 2.7m                  & 92.4           &   87.2    &   82.6      \\
    \bottomrule
  \end{tabular}
\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. Params.\ is the approximate number of trained parameters (excluding word embeddings for all models). Trans.\ acc.\ is the model's accuracy in predicting parsing transitions at test time. Train and test are SNLI classification accuracy.}
\end{table*}

@@

Because this paper aims to introduce a general purpose model for sentence encoding, we do not pursue the use of soft attention \citep{bahdanau2014neural,rocktaschel2015reasoning}, despite its demonstrated effectiveness on the SNLI task.\footnote{Attention-based models like \citet{rocktaschel2015reasoning}, \citet{wang2015learning}, and the unpublished \citet{cheng2016long} have shown accuracies as high as 86.3\% on SNLI, but are more narrowly engineered to suit the task and do not yield sentence encodings.} However, we expect that it should be possible to productively combine our model with soft attention to reach state-of-the-art performance.
